Inference using context-dependent models of mutation

### 2017-04-26 writeups/context-dependence.tex
moved writeup-plots/
re-found figures for tex writeup

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{../tasep/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates for six different data sets of the parameter in TASEP (mutation rate multiplied by time).
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{../writeup-plots/selsims-2013-05-28-17-12-0275615-traces}
  \end{center}
  \caption{
  MCMC traces of the parameters in the Ising model across 100,000 iterations.
  The units of $\lambda$ are in mean number of changes per site.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=1]{../ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the time-scaled mutation rate parameter $\lambda t$,
  in ten different simulated datasets under the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=2]{../ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the inverse temperature $\beta$ in the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=3]{../ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the magnetization parameter $\beta$ in the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{../writeup-plots/selsims-2013-06-03-13-17-0790276-initfreqs}
  \end{center}
  \caption{
  MCMC traces across 660,000 iterations of the frequencies at the root of the (two-taxon) tree in the CpG model.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{../writeup-plots/selsims-2013-06-03-13-17-0790276-mutrates}
  \end{center}
  \caption{
  MCMC traces across 660,000 iterations of several mutation rate parameters in the CpG model.
  Units are in mean number of substitutions per base across the entire tree.
  Vertical line shows the true value.
  }
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{writeup-plots/tasep_all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates for six different data sets of the parameter in TASEP (mutation rate multiplied by time).
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{writeup-plots/selsims-2013-05-28-17-12-0275615-traces}
  \end{center}
  \caption{
  MCMC traces of the parameters in the Ising model across 100,000 iterations.
  The units of $\lambda$ are in mean number of changes per site.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=1]{writeup-plots/ising_all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the time-scaled mutation rate parameter $\lambda t$,
  in ten different simulated datasets under the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=2]{writeup-plots/ising_all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the inverse temperature $\beta$ in the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=3]{writeup-plots/ising_all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the magnetization parameter $\beta$ in the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{writeup-plots/selsims-2013-06-03-13-17-0790276-initfreqs}
  \end{center}
  \caption{
  MCMC traces across 660,000 iterations of the frequencies at the root of the (two-taxon) tree in the CpG model.
  Vertical line shows the true value.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{writeup-plots/selsims-2013-06-03-13-17-0790276-mutrates}
  \end{center}
  \caption{
  MCMC traces across 660,000 iterations of several mutation rate parameters in the CpG model.
  Units are in mean number of substitutions per base across the entire tree.
  Vertical line shows the true value.
  }
\end{figure}
